% Acknowledgments

\documentclass[main.tex]{subfiles}
\begin{document}

\chapter*{Acknowledgments}
{
\setlength{\parindent}{0cm}
\setlength{\parskip}{12pt}
Thank you Prof. Rudolph and Prof. Osswald for your trust and patience. I couldn't hope for better advisors.
     
Thank you Tom for your extrusion expertise and your polymer knowledge. The sass that came attached to your friendship was OK too I suppose.

Thank you Luke for building the tools necessary for this whole project to work. That big beard hides a sharp mind -and a lot of patience to answer all my random grammar questions.

Thank you Alec for being an ever-present helping hand, a great classmate, and a good friend. Hope you make ND proud. Keep it up and one day you'll get your \emph{full 15 seconds of screen time} in a Hockey game.

Thank you Jos\'e for putting up with my constant interruptions \emph{en espa\~nol} from across the desk, and for sharing lab managing duties with me. Suerte y paciencia para el doctorado. 

Thank you to Thibaut, Colby, Johannes, Peilin and Brendan. This thesis would look very empty without your contributions!
    
Thank you to the entire PEC family for creating a great learning environment. I've grown so much with all of you. I hope that you've learned a thing or two with me as well.

Thank you to Ben, Josh, Diego, Iv\'an, Pfeifer, Ian, Maria, Sianna and Sara for your friendship. Madison was a lot of fun because you were in it.

Gracias a mi familia, a quienes les debo todo. Alejandro, Luana y Gabriel: veo en ustedes inteligencia y carisma que sobrepasan las m\'ias. \'Usenlas acompa\~nadas de dedicaci\'on y llegar\'an m\'as lejos que su hermano mayor, que los quiere mucho. 

Gracias a Sonya por tu cari\~no y paciencia. Que este tiempo que pasamos tan lejos nos traiga en creces momentos juntos. Te amo.  
}
\end{document}